CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-27 paper_I/ms.tex
paper update figs

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{avg_acf.pdf}
	\end{center}
	\vspace{-0.5cm}
  \caption{
    Average autocorrelations of $10^4$ randomly selected light curves
    from each sector.  The medians at time lags spaced by one hour are
    shown for raw light curves (column name \texttt{IRM}) in gray, and
    for TFA-detrended light curves in black.  The gray bands display
    the 25$^{\rm th}$ to 75$^{\rm th}$ percentile range for each type
    of light curve.
  \label{fig:avg_acf}
	}
\end{figure}

@@

The on-sky locations of the light curves from Sectors 6 and 7 are
shown in Figure~\ref{fig:lcgalactic}.  Black stars are the field stars
for which we performed photometry, and of which a subset were used as
template stars during TFA.  The blue stars are the \numberlcs stars
with light curves available from \stscilink.  Most of the target stars
are quite close to the galactic plane.  Gaps between CCD chips are
also visible.  The highly clumped nature of the target stars is also
apparent.

%A zoom-in of Figure~\ref{fig:lcgalactic} is shown in Figure~\ref{fig:lcradeczoom}
%for the Camera 1, Sector 6 field. The effects of galactic-latitude
%dependent extinction are visible through the decreasing density of black
%points towards the right of the image.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of TESS
$T$-band magnitudes for the target stars.  Though most of the targets
are faint, $\approx3\times10^4$ are brighter than $T=13$. These
targets are more promising for any detailed follow-up observtions.

An HR diagram for the entire sample of CDIPS stars on silicon is shown
in Figure~\ref{fig:hrd} (top).  The sub-sample of stars with measured
positive parallaxes and naive distances less than $1\,{\rm kpc}$ is
also shown (bottom).  About one-third of the stars are in this latter
sample.  The close stars are predominantly on the main-sequence, or
the pre-main-sequence.  A relatively large fraction of these come from
\citet{zari_3d_2018}, and are either on the PMS or upper
main-sequence.  The latter set of OBA dwarf stars, while ``younger''
than the typical field dwarf, are likely the least interesting subset
of our target sample from the perspective of age analyses.  In the
entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of
stars are sub-giants, red giants, and helium-burning red-clump stars.
We failed to obtain light curves for roughly $5\%$ of the stars on
silicon, primarily due to our masking of saturated stars and their
nearby pixels.

Finally, Figure~\ref{fig:propermotions} shows the proper motions of
the entire and close samples of stars on silicon.  Each clump
signifies a different star cluster. The largest overdensity in the top
figure is composed mainly of field star contaminants. It has two
subcomponents, due to the two different directions in the Galaxy being
observed in Sectors 6 and 7.

>>>>

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.97\textwidth]{avg_acf.pdf}
	\end{center}
	\vspace{-0.5cm}
  \caption{
    Average autocorrelations of $10^4$ randomly selected light curves
    from each sector.  The medians at time lags spaced by one hour are
    shown for raw light curves (column name \texttt{IRM}) in gray, and
    for TFA-detrended light curves in black.  The gray bands display
    the 25$^{\rm th}$ to 75$^{\rm th}$ percentile range for each type
    of light curve.
  \label{fig:avg_acf}
	}
\end{figure*}

@@

The on-sky locations of the light curves from Sectors 6 and 7 are
shown in Figure~\ref{fig:lcgalactic}.  Black stars are the field stars
for which we performed photometry, and from which we selected template
stars for TFA, as well as the construction of the PCA eigenvectors.
Blue points are the \numberlcs stars with light curves available from
\stscilink.  Most of the target stars are quite close to the galactic
plane.  Gaps between CCD chips are also visible.  The highly clumped
nature of the target stars is also apparent.

Figure~\ref{fig:cdf_T_mag} shows the cumulative distribution of TESS
$T$-band magnitudes for the target stars.  Though most of the targets
are faint, $\approx3\times10^4$ are brighter than $T=13$. The brighter
targets will be more amenable to detailed spectroscopic observtions,
should the need arise.

An HR diagram for the entire sample of CDIPS stars on silicon is shown
in Figure~\ref{fig:hrd} (top).  The sub-sample of stars with measured
positive parallaxes and naive distances less than $1\,{\rm kpc}$ is
also shown (bottom).  About one-third of the stars are in this latter
sample.  Of the close stars, a relatively large fraction come from
\citet{zari_3d_2018}, and are either on the PMS or upper
main-sequence.  The latter set of OBA dwarf stars, while ``younger''
than the typical field dwarf, are likely the least interesting subset
of our target sample from the perspective of age analyses.  In the
entire sample (Figure~\ref{fig:hrd} top), a much larger fraction of
stars are sub-giants, red giants, and helium-burning red-clump stars.

Finally, Figure~\ref{fig:propermotions} shows the proper motions of
the entire and close samples of stars on silicon.  Each clump
signifies a different star cluster. The large overdensity in the top
panel is composed mainly of field star contaminants. It has two
subcomponents, due to the two different directions in the Galaxy being
observed in Sectors 6 and 7.
